---
title: "Templating"
output: rmarkdown::html_vignette
description: |
    Templating is the a quick investigation of setting up templates.
vignette: >
  %\VignetteIndexEntry{Templating}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

When handling data-input for R and Python analyses, I have a few very common workflows.
* Load data from a specific source as is:
    * Could be from disk
	* Could be from website / S3

* Runs scripts in another environment (typical an SQL server of some kind) to produce data.
    * I often cache these on disk then to avoid re-running the computing code

I previously specified the file and data-paths individually in R and Python as needed but it made switching between the two
slow, complicated and painful. It is easier to define a simple shared format and then define a package for each language that can parse it to the required
format to successfully load the data.


```{r setup}
library(dataIngestFormatR)
dataIngestFormatR::hello()  # Test no-action print function works for install and exports to all be working
```

We can then look at a few exmaple YAML files and how this package would parse them.

Please note that the package does not itself load all of the data. That is handled separately. This package loads the information needed to inform loading the data.

## YAML specifying loading from disk

```{r disk_example}
disk_yaml_snippet <- ""
```

## YAML specifying loading the data via running SQL and pulling data over an ODBC connection

```{r sql_example}
sql_yaml_snippet <- ""
```

## YAML - from website download
```{r web_download}
web_download_yaml_snippet <- ""
```

## YAML - from S3
```{r s3_download}
s3_download_yaml_snippet <- ""
```
